### 2025-04-02 chapters/conclusion.tex
Initial commit

% ==============================================
\chapter{Conclusions}
% ==============================================
\markboth{\bf Chapter \thechapter: Conclusions}{}
\label{sec:Conclusions}

% ============================
% In this work, we
% ============================

% ============================
% Future Directions
% ============================

>>>>

% ==============================================
\chapter{Conclusions}
% ==============================================
\markboth{\small \textsc{Chapter \thechapter}: \bf Conclusions}{}
\label{sec:Conclusions}

\epigraph{
    \textit{Ignoramus et ignorabimus}

    [We do not know and we will not know]
}{
    Maxim on the limits of knowledge
}

\epigraph{
    \textit{Wir m\"ussen wissen -- wir werden wissen}.
    %
    [We must know -- we will know.]
}{
    \href{smith-at-sfsu.net/Documents/HilbertRadio/HilbertRadio.mp3}{David Hilbert, in response}
}

\epigraph{
    Do not condescend to ask:
    %
    ``Shall we conquer? Shall we be conquered?''
    %
    Fight on!
}{
    Nikos Kazantzakis
}

In this thesis, we studied perturbative manifestations and phenomenological probes of quantum chromodynamics (\gls{qcd}) in particle collisions.
%
After discussing the how quarks and gluons are the building blocks of the vast majority of our visible universe and the basics of \vocab{partonic scattering} in \Chap{particles} and the \vocab{partonic cascade model} for jet formation and substructure in \Chap{jets}, we realized that the real world presented greater challenges.
%
In particular, we understood that tests of our parton-level predictions of perturbative \gls{qcd} (\gls{pqcd}) require us to overcome the presence of \vocab{low-energy pollution}:
%
\gls{hadronization} and \gls{deteffects} (soft distortions) as well as the \glslink{ue}{underlying event} and \glslink{pileup}{pileup} (additive contamination).
%
With the tools of \gls{pqcd} honed in our introductory chapters, we undertook the task of \vocab{\gls{jet-grooming}} in \Chap{grooming}, where we explicitly removed soft radiation from jets in order to access high-energy, pollution-free degrees of freedom.
%
We began by building intuition for traditional hard-cutoff methods for grooming before building the framework of \PIRANHA{} for continuous grooming and showcasing its formal and phenomenological strengths.
%
Finally, in \Chap{ewocs}, we explored the techniques of \vocab{energy-weighted correlation functions}, with the goal of \textit{ignoring} the low-energy effects of pollution through energy weighting.
%
We introduced the basic theory of the energy-energy correlator (\gls{eec}) for probing angular correlations in collision events, discussed its efficient and visually intuitive higher point generalizations, and even initiated the study of \vocab{energy-weighted observable correlations} (\glspl{ewoc}) to probe arbitrary non-angular correlations, such as the pair-wise masses of subjets.

It has been a privilege to explore the universe with you.
%
Our goal has been to develop realistic tools for the study of the most fundamental features of our universe that humanity has been able to experimentally probe.
%
Our method was to develop collider observables whose behavior illuminates the structure of \gls{qcd} even through the obfuscating haze of contamination generated both by theoretical and experimental effects.
%
As stated by Andrew Larkoski, ``the art of jet substructure... is in the construction of observables'' \cite{}.
%
With the impressionist exposition and few new brush strokes presented in this thesis, we hope we have been able to share our sincere appreciation of the arts of jet substructure and quantum field theory.
%
A more precise understanding of the tools we presented here will require further, finer brush strokes:
%
precision calculations, experimental measurements, the modelling of theoretical and experimental uncertainties, and beyond.
%
But those tales are for another day, and another teller.

### 2025-04-02 frontmatter/notation.tex
Initial commit

% =====================================
\section*{Notation and Terminology}
% =====================================
\markboth{Notation and Terminology}{}

@@

\begin{sambox}{Some TODOs for Sam}{}
    \begin{itemize}
        \item
            Is there a proof that pdfs and fragmentation functions are universal?
            %
            Should put this in somewhere...

        \item
            \sam{Does fragmentation belong in a place where pdfs can fit in..?
                %
                Seems like factorization is the actual important piece. But my thesis is not about factorization!
                %
                I need to find a tasteful way to include it.
            }

        \item
            \sam{Need to fix header on problem pages, which simply use the most recent appendix instead.}
    \end{itemize}
\end{sambox}

Here is some common, and relatively important, notation used throughout this thesis.
%
See \Sec{morenotation} for a more comprehensive list.

\begin{itemize}
    \item
        A \vocab{calcule} is a small calculation, often a simple example or a part of a bigger calculation.

    \item
        \(\eqdelta\) denotes equality by definition;

@@

    \item
        The \textit{energy fraction} carried by a particular particle in a scattering event or jet, relative to the total energy of the event or jet, will play an important role in this thesis.
        %
        We will use the symbol \(z_i\) to denote the energy fraction particle \(i\) within a jet or event:
        \begin{align}
            z_i
            \eqdelta
            \frac{E_i}{E_\text{tot}}
            .
        \end{align}

    \item
        A useful definition for clarity is that of the value of \(\alpha_s\) divided by \(4\pi\), since this quantity appears in loop computations (which often have a \(4\pi\) suppression):
        \begin{subequations}
        \begin{align}
            a_s = \frac{\alpha_s}{4\pi}
        \end{align}
        \end{subequations}
\end{itemize}

>>>>

% =====================================
\section*{Notation and Terminology}
% =====================================
% \markboth{Notation and Terminology}{Notation and Terminology}

\epigraph{If you think this Universe is bad, you should see some of the others.}{Philip K. Dick}

@@

\begin{sambox}{Some TODOs for Sam}{}
    \begin{itemize}
        \item
            Need to fix header on problem pages, which simply use the most recent appendix instead.

        \item
            List of problems

        \item
            Signature page

        \item
            Add epsilon UV/IR calculations involving EEC

        \item
            Unify notation of epigraphs, probably want names then titles
    \end{itemize}
\end{sambox}

Here is some common notation used throughout this thesis.
%
See \Sec{morenotation} for a more comprehensive list.

\begin{itemize}
    \item
        A \vocab{calcule} is a smaller analogue of a calculation (such as a simple example or a part of a bigger calculation)

    \item
        \(A := B\) means ``\(A\) is defined to mean \(B\)'', as does \(B =: A\);

@@

    \item
        The \textit{energy fraction} carried by a particular particle in a scattering event or jet, relative to the total energy of the event or jet, will play an important role in this thesis.
        %
        We will use the symbol \(z_i\) to denote the energy fraction particle \(i\) within a jet or event:
        \begin{align}
            z_i
            \eqdelta
            \frac{E_i}{E_\text{tot}}
            .
        \end{align}
        \sam{Revisit}

    \item
        We will also use the following standard definitions:
        \begin{subequations}
        \label{eq:qcd_coupling}
        \begin{align}
            \label{eq:as_defn}
            \as &= \frac{\alpha_s}{4\pi}
            \\
            \label{eq:beta_fn_defn}
            \frac{\dd}{\dd\log\mu}\alpha_s(\mu)
            &\eqdelta
            \beta(\alpha_s)
            =
            -2\beta_0 \alpha_s(\mu)^2 + \mathcal{O}\le(\alpha_s(\mu)^3\ri)
            \\
            \label{eq:alphas_1loop}
            \alpha_s^\text{(1-loop)}(\mu)
            &=
            \frac{\alpha_s(Q)}{1 + 2\alpha_s(Q) \beta_0 \log(\frac{\mu}{Q})}
            ,
        \end{align}
        where
        \begin{align}
            \beta_0 = \frac{1}{12\pi}\le(11\,C_A - 4\,T_f n_f\ri)
        \end{align}
        \end{subequations}
        is the leading coefficient of the QCD beta function, \(n_f = 5\) denotes the number of effectively massless quark flavors, \(Q\) indicates a reference scale (such as the energy scale of a hard process), and
        \begin{subequations}
        \label{eq:group_theory}
        \begin{align}
            C_F &= \frac{N_c^2 - 1}{2N_c}
            % \xrightarrow[]{\text{QCD}}
            % \frac{4}{3}
            \\
            C_A &= N_c
            % \xrightarrow[]{\text{QCD}}
            % 3
            \\
            T_F &= \frac{1}{2}
            ,
        \end{align}
        \end{subequations}
        denote the quadratic Casimir for the fundamental representation of \(SU(N_c)\), the quadratic Casimir for the adjoint representation, and the Dynkin index of the fundamental representation, respectively.
        %
        The expressions of \Eq{group_theory} are often referred to collectively as \textit{group theory factors}.
        %
        For QCD, \(N_c = 3\), \(C_F = 4/3\), and \(C_A = 3\), giving \(
            \beta_0 = \le(11 - 2 n_f / 3\ri)/4\pi
            .
        \)

%         A useful definition for clarity is that of the value of \(\alpha_s\) divided by \(4\pi\), since this quantity appears in loop computations (which often have a \(4\pi\) suppression):
%         \begin{subequations}
%         \begin{align}
%             a_s = \frac{\alpha_s}{4\pi}
%         \end{align}
%         \end{subequations}
\end{itemize}

Furthermore, we will assume
\begin{itemize}
    \item
    That all partons other than the top quark are massless;

    \item
    That we may ignore electroweak effects (i.e. perform calculations without the \(W\) and \(Z\) bosons).
\end{itemize}

### 2025-04-02 frontmatter/preface.tex
Initial commit

\section*{Preface}
\markboth{Preface}{}

>>>>

\section*{Preface}
% \markboth{Preface}{Preface}

\sam{Goal: in a couple of (concerted) weeks, you can master what took me six years (to the extent that I have mastered it)!}

\begin{itemize}
    \item
        Chapters/sections XXX are good for learning

    \item
        My main contributions presented in this thesis are the introduction of \textsc{Piranha} as a paradigm for continuous grooming (\Secs{}{}), the development of new, efficient, and visually intuitive tools for higher-point energy correlators (\Sec{}), and the introduction of the theory of Energy-Weighted Observable Correlations (EWOCs) as a generalization of energy correlators (\Sec{}).
\end{itemize}

\sam{Address Jesse's concerns}

### 2025-04-02 frontmatter/prerequisites.tex
Initial commit

\section*{Prerequisites}
\markboth{Prerequisites}{}

@@

>>>>

\section*{Prerequisites}
% \markboth{Prerequisites}{Prerequisites}

@@

In addition, since we are lucky enough to live in the age of free internet resources, I will mention the following incredible texts:

\textbf{Basics of Quantum Field Theory:}
\begin{itemize}
    \item
        \underline{Book name}, by \sam{author}

        This book \sam{does ...}

        Available at \sam{place/url}
\end{itemize}

\textbf{Specific References for QCD:}
\begin{itemize}
    \item
        \underline{Applications of Perturbative QCD}, by Richard D. Field;

        This book \sam{does ...}

        Of course, it would be a shame to access this book quickly, easily, and for free using \url{libgen.is}, so I will mention that it is also available (at time of writing) at \href{https://www.desy.de/~jung/qcd_and_mc_2009-2010/R.Field-Applications-of-pQCD.pdf}{this desy.de link}.
\end{itemize}
